class: inverse,middle,center 

# plotDist

---

class: split-four


<!--column 1-->

.column[
.split-three[
.row[
```{r, fig.asp=.57 }
plotDist("norm")
```
]
.row[
```{r , fig.asp=.57}
plotDist("norm",type="h")
```
]
.row[
```{r , fig.asp=.57}
plotDist("norm",kind="cdf")
```
]

]]
 

<!--column 2-->

.column[
.split-three[
.row[
```{r, fig.asp=.57 }
plotDist("norm", mean=10, sd=2)
```
]
.row[
```{r , fig.asp=.57}
plotDist("norm", mean=10, sd=2, col="green", type="h" )
```
]
.row[
```{r , fig.asp=.57}
plotDist("binom",25,.25)
```
]

]]
 

<!--column 3-->

.column[
.split-three[
.row[
```{r, fig.asp=.57 }
plotDist('binom',params=list(25,.25))
```
]
.row[
```{r , fig.asp=.57}
plotDist("exp")
```
]
.row[
```{r , fig.asp=.57}
plotDist("exp", kind='histogram')
```
]

]]

<!--column 4-->
  
.column[
.split-three[
.row[
```{r, fig.asp=.57 }
plotDist("chisq", df=4, groups= x > 6) 
```
]
.row[
```{r , fig.asp=.57}
plotDist("f",df1=1, df2=99)
```
]
.row[
```{r , fig.asp=.57}
plotDist("t", df=99)
```
]

]]



---

class: inverse,middle,center 

# plotFun

---

class: split-four


<!--column 1-->

.column[
.split-three[
.row[
```{r, fig.asp=.57 }
plotFun(x^2~x,xlim=range(-5,5))
```
]
.row[
```{r , fig.asp=.57}
plotFun(x^3~x,xlim=range(-5,5))
```
]
.row[
```{r , fig.asp=.57}
plotFun(x^4~x,xlim=range(-5,5))
```
]

]]
 

<!--column 2-->

.column[
.split-three[
.row[
```{r, fig.asp=.57 }
plotFun(5/x~x,xlim=range(-5,5))
```
]
.row[
```{r , fig.asp=.57}
plotFun(sqrt(25-x^2)~x,xlim=range(-5,5))
```
]
.row[
```{r , fig.asp=.57}
plotFun(2*x+3~x,xlim=range(-5,5))
plotFun(x^2~x,xlim=range(-5,5), add=T)
```
]

]]
 

<!--column 3-->

.column[
.split-three[
.row[
```{r, fig.asp=.57 }
plotFun( x^2 -3 ~ x, xlim=c(-4,4), grid=TRUE )
ladd( panel.abline(h=0,v=0,col='gray50') )
plotFun( (x^2 -3) * (x^2 > 3) ~ x, type='h', alpha=.1, lwd=4, col='lightblue', add=TRUE )
```
]
.row[
```{r , fig.asp=.57}
```
]
.row[
```{r , fig.asp=.57}
```
]

]]

<!--column 4-->
  
.column[
.split-three[
.row[
```{r, fig.asp=.57 }

```
]
.row[
```{r , fig.asp=.57}
```
]
.row[
```{r , fig.asp=.57}
```
]

]]



---

class: split-four


<!--column 1-->

.column[
.split-three[
.row[
```{r, fig.asp=.57 }
pnorm(650,500,100)
```
]
.row[
```{r , fig.asp=.57}
xpnorm(650,500,100, return="plot")
```
]
.row[
```{r , fig.asp=.57}
xpnorm(-3:3, return="plot", system="gg")  
```
]

]]
 

<!--column 2-->

.column[
.split-three[
.row[
```{r, fig.asp=.57 }
xpnorm(-3:3, return="plot", system="gg")  %>% 
    gf_labs(title="My plot", x="") %>% 
    gf_theme(theme_minimal())
```
]
.row[
```{r , fig.asp=.57}
xqnorm(.75, 500, 100, return="plot")
```
]
.row[
```{r , fig.asp=.57}
zscore(rnorm(100, mean=30,sd=6)) %>% 
    head(20)
```
]

]]
 

<!--column 3-->

.column[
.split-three[
.row[
```{r, fig.asp=.57 }
findZeros( sin(t) ~ t, xlim=c(-10,10) )
```
]
.row[
```{r , fig.asp=.57}
solve(4*x+4==0 ~ x)
```
]
.row[
```{r , fig.asp=.57}
CIsim(n=10, samples=200)
```
]

]]

<!--column 4-->
  
.column[
.split-three[
.row[
```{r, fig.asp=.57 }
confint(t.test(rnorm(100)))
```
]
.row[
```{r , fig.asp=.57}
pval(t.test(rnorm(100)))
```
]
.row[
```{r , fig.asp=.57}
stat(t.test(rnorm(100)))
```
]

]]


---

.pull-left[
```{r pdist1,fig.asp=.41, out.width="100%"}
pdist(q=1.96,  return="plot")
```
```{r pdist2,fig.asp=.41, out.width="100%"}
pdist(q=1.96,  return="values")
```

]


.pull-right[

```{r pdist3, fig.asp=.41}
pdist(q=1.96, plot = FALSE  )
```
```{r pdist4, fig.asp=.41}
pdist(q=1.96, verbose = TRUE)
```

]

---

.pull-left[
```{r pdist5,fig.asp=.41}
pdist(q=1.96,  invisible=TRUE)
```
```{r pdist6,fig.asp=.41}
pdist(q=1.96,  lower.tail=F)
```
]


.pull-right[

```{r pdist7, fig.asp=.41}
pdist(q=-2:2)
```
```{r pdist8, fig.asp=.41}
pdist(q=seq(80,120,10), mean=100,sd=10)
```

]

---

.pull-left[
```{r pdist9,fig.asp=.41}
pdist(q=c(-1.96,1.96),refinements = list(mytheme))
```
```{r pdist10,fig.asp=.41}
qdist(p=c(.025,.975),mean=30000,sd=2500)
```
]


.pull-right[

```{r pdist11, fig.cap="two-tailed with mean 30000" ,fig.asp=.41}
pdist(q=c(25000,35000),mean=30000,sd=2500,refinements = list(mytheme))
```
```{r pdist12, fig.asp=.41}
pdist(q=34899,mean=30000,sd=2500)
```

]

---

## Right tail

.pull-left[

```{r qdist2,fig.asp=.41, eval=F}
qr05 <- qdist(p=.950,mean=30000,sd=2500, plot=F)
ql05 <- qdist(p=.050,mean=30000,sd=2500, plot=F) + 4000
yr1 <- .000008
yr2 <- .000045
xr1 <- qr05 + 1000
xr2 <- qr05 + 3000
yl1 <- .000084
yl2 <- .000100
xl1 <- ql05 - 1000
xl2 <- ql05 - 5000
themeL05  <-  list(annotate("curve",curvature=-0.3, 
			    x=xr1,y=yr1,xend=xr2,yend=yr2, 
			    alpha=0.3, 
			    arrow=arrow(length=unit(2,"mm"))),
			 annotate("text",
				  x=xr2+400,
				  y=yr2,
				  label=".05") ,
                         annotate("curve",alpha=0.3,
				  curvature=0.3, 
				  x=xl1,y=yl1,xend=xl2,yend=yl2,
				  arrow=arrow(length=unit(2,"mm"))),
			 annotate("text",x=xl2-400,y=yl2,label=".95"))


pdist(q=qr05,mean=30000,sd=2500, return="plot", 
      refinements = list(mytheme,
			 scale_x_continuous(breaks=c(25000,30000,34112),
					    labels=c("25000", 
						     expression(paste(mu,"=30000")),"34112")),
			 geom_vline(color="red",xintercept=30000),
			 themeL05)
)
```
]


.pull-right[

```{r qdist2-out,  ref.label="qdist2", echo=F }
```

]


---

## Left tail

.pull-left[

```{r qdist3,fig.asp=.41, eval=F}
mu <- 30000
stdev <- 2500
qr05 <- qdist(p=.950,mean=mu,sd=stdev, plot=F)
ql05 <- qdist(p=.050,mean=mu,sd=stdev, plot=F) 
yr1 <- .000008
yr2 <- .000045
xr1 <- qr05 + 1000
xr2 <- qr05 + 3000
yl1 <- .000084
yl2 <- .000100
xl1 <- ql05 + 3000
xl2 <- ql05 - 1000

themeR05  <-  list(annotate("curve",curvature=-0.3, 
			    x=xr1,y=yr1,xend=xr2,yend=yr2, 
			    alpha=0.3, 
			    arrow=arrow(length=unit(2,"mm"))),
			 annotate("text",
				  x=xr2+400,
				  y=yr2,
				  label=".05") ,
                         annotate("curve",alpha=0.3,
				  curvature=0.3, 
				  x=xl1,y=yl1,xend=xl2,yend=yl2,
				  arrow=arrow(length=unit(2,"mm"))),
			 annotate("text",x=xl2-400,y=yl2,label=".95"))

pdist(q=qr05,mean=mu,sd=stdev, return="plot", 
      refinements = list(mytheme,
			 scale_x_continuous(breaks=c(ql05,mu,qr05),
					    labels=c(round(ql05), 
						     expression(paste(mu,"=30000")),round(qr05))),
			 geom_vline(color="red",xintercept=30000),
			 themeR05)
)
```
]


.pull-right[

```{r qdist3-out,  ref.label="qdist3", echo=F }
```

]


---

## Two tail

.pull-left[

```{r qdist4,fig.asp=.41, eval=F}
mu <- 30000
stdev <- 2500
qr025 <- qdist(p=.975,mean=mu,sd=stdev, plot=F)
ql025 <- qdist(p=.025,mean=mu,sd=stdev, plot=F) 
yl1 <- .000008
yl2 <- .000045
xl1 <- ql025 - 1000
xl2 <- ql025 - 3000
yr1 <- .000008
yr2 <- .000045
xr1 <- qr05 + 1000
xr2 <- qr05 + 3000
ym1 <- .000100
ym2 <- .000144
xm1 <- mu + 1000
xm2 <- mu + 3000


theme2_05  <-  list(annotate("curve",curvature=-0.3, 
			    x=xr1,y=yr1,xend=xr2,yend=yr2, 
			    alpha=0.3, 
			    arrow=arrow(length=unit(2,"mm"))),
			 annotate("text",
				  x=xr2+400,
				  y=yr2,
				  label=".025") ,
                         annotate("curve",alpha=0.3,
				  curvature=0.3, 
				  x=xl1,y=yl1,xend=xl2,yend=yl2,
				  arrow=arrow(length=unit(2,"mm"))),
			 annotate("text",x=xl2-400,y=yl2,label=".025"),
                         annotate("curve",alpha=0.3,
				  curvature=-0.3, 
				  x=xm1,y=ym1,xend=xm2,yend=ym2,
				  arrow=arrow(length=unit(2,"mm"))),
			 annotate("text",x=xm2+400,y=ym2,label=".95")


                         )

pdist(q=c(ql025,qr025),mean=mu,sd=stdev, return="plot", 
      refinements = list(mytheme,
			 scale_x_continuous(breaks=c(ql025,mu,qr025),
					    labels=c(round(ql025), 
						     expression(paste(mu,"=30000")),round(qr025))),
			 geom_vline(color="#FDE725",xintercept=mu),
			 theme2_05)
)
```
]


.pull-right[

```{r qdist4-out,  ref.label="qdist4", echo=F }
```

]


---





## qdist()

```{r qdist}
qdist(p=0.975)
```


---

## Breaks

.pull-left[
```{r ,fig.asp=.41}
x <- rbinom(100, 100, 0.4)
p <- gf_bar( ~ x)
p %>% 
 gf_refine(scale_x_continuous(breaks = discrete_breaks()))
```
```{r ,fig.asp=.41}
p %>% 
 gf_refine(scale_x_continuous(breaks = discrete_breaks(5)))
```
]


.pull-right[

```{r , fig.asp=.41}
p %>% 
 gf_refine(scale_x_continuous(breaks = discrete_breaks(2)))
```
]


---

## abline 


.pull-left[

```{r }
mtcars2  <- df_stats(wt ~ cyl, data=mtcars, median_wt=median)
mtcars2
```
```{r ,fig.asp=.41}
gf_point(wt ~ hp, size = ~wt, color= ~cyl, data = mtcars) %>% 
    gf_abline(slope = ~0, intercept=~median_wt, color=~cyl, data=mtcars2) 
```
]


.pull-right[

```{r , fig.asp=.41}
```
```{r , fig.asp=.41}
```
]


class: split-four

<!--column 1-->

.column[
.split-three[
.row[
```{r, fig.asp=.57 }
plotDist("norm")
```
]
.row[
```{r , fig.asp=.57}
plotDist("norm",type="h")
```
]
.row[
```{r , fig.asp=.57}
plotDist("norm",kind="cdf")
```
]

]]
 

<!--column 2-->

.column[
.split-three[
.row[
```{r, fig.asp=.57 }
plotDist("norm", mean=10, sd=2)
```
]
.row[
```{r , fig.asp=.57}
plotDist("norm", mean=10, sd=2, col="green", type="h" )
```
]
.row[
```{r , fig.asp=.57}
plotDist("binom",25,.25)
```
]

]]
 

<!--column 3-->

.column[
.split-three[
.row[
```{r, fig.asp=.57 }
plotDist('binom',params=list(25,.25))
```
]
.row[
```{r , fig.asp=.57}
plotDist("exp")
```
]
.row[
```{r , fig.asp=.57}
plotDist("exp", kind='histogram')
```
]

]]

<!--column 4-->
  
.column[
.split-three[
.row[
```{r, fig.asp=.57 }
plotDist("chisq", df=4, groups= x > 6) 
```
]
.row[
```{r , fig.asp=.57}
plotDist("f",df1=1, df2=99)
```
]
.row[
```{r , fig.asp=.57}
plotDist("t", df=99)
```
]

]]





