---
title: "Demo of wbstats packages"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu,"myprez.css"]
    nature:
      ratio: 16:10
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

class: inverse,middle,center

## Regular expression demo

---

```{r setup, include = F}

knitr::opts_chunk$set(fig.width = 6, 
		      message = FALSE, 
		      warning = FALSE, 
		      comment = "", 
		      cache = FALSE, 
		      fig.retina = 3)

library(tidyverse)
library(flipbookr)
library(wbstats)
library(rmarkdown)
```

```{r wb1}
str(wb_cachelist, max.level=1)
```

**Accessing updated data**

```{r}
new_cache <- wbcache()
```

Find the unemployment rate data 

```{r}
gdp_growth_vars <- wbsearch(pattern="gdp growth")
uemploy_vars=wbsearch(pattern="Unemployment rate in total population")
poverty=wbsearch(pattern="poverty rate")
unN_rate <- str_subset(uemploy_vars$indicatorID, "ccx_un")
ur <- wb(country=c("IN"), indicator=unN_rate,mrv=10)
ur <- wb(country=c("IN"), indicator='EG.ELC.ACCS.ZS',mrv=3)
health <- wb(country="BD",indicator=c("SH.XPD.CHEX.GD.ZS"),mrv=3)
health <- WDI(country=c("BD"),indicator=c("SH.XPD.CHEX.GD.ZS"))
health.wdi.vars  <- wbsearch(pattern="health.*gdp")
health.fac  <- wbsearch(pattern="health")
health.wdi.vars.wb <- WDIsearch("health.*gdp")
```


---

Finally some sort of breakthrough

Found that with new_cache we can actuallly access the data 


```{r}
new_cache   <- wbcache() 
health <- wb(country="countries_only",indicator=c("SH.XPD.CHEX.GD.ZS"),mrv=1, cache=new_cache)
health_reg <- wb(country="aggregates",indicator=c("SH.XPD.CHEX.GD.ZS"),mrv=1, cache=new_cache)
```

South Asian countries 

```{r}
south.asia <- c("BD","IN","PK","LK","AF","NP","BT","MV","MM")
health.sa<- health %>% 
		 filter(iso2c %in% south.asia) %>% 
                 select(country, value) %>% 
		 arrange(-value)
health.sa
```

Top 20 countries 

```{r}
health %>% 
    select(date, iso2c,country, value) %>% 
		 arrange(-value) %>% 
		 slice(1:20)

```

Bottom 20 countries 

```{r}
health %>% 
    select(date, iso2c,country, value) %>% 
		 arrange(value) %>% 
		 slice(1:20)

```

```{r}
health %>% 
    select(date, iso2c,country, value) %>% 
		 arrange(-value) %>% 
		 tail(20)
		 

```

Military expenditure 


```{r}
military_vars =wbsearch(pattern="military expenditure.*gdp")
military_vars
```



```{r}
new_cache   <- wbcache() 
military <- wb(country="countries_only",indicator=c("MS.MIL.XPND.GD.ZS"),mrv=1)
military_reg <- wb(country="aggregates",indicator=c("MS.MIL.XPND.GD.ZS"),mrv=1, cache=new_cache)
```

South Asian countries 

```{r}
south.asia <- c("BD","IN","PK","LK","AF","NP","BT","MV","MM")
military.sa<- military %>% 
		 filter(iso2c %in% south.asia) %>% 
                 select(country, value) %>% 
		 arrange(-value)
military.sa
```

Top 20 countries 

```{r}
military %>% 
    select(date, iso2c,country, value) %>% 
		 arrange(-value) %>% 
		 slice(1:20)

```

Bottom 20 countries 

```{r}
military %>% 
    select(date, iso2c,country, value) %>% 
		 arrange(value) %>% 
		 slice(1:20)

```

```{r}
military %>% 
    select(date, iso2c,country, value) %>% 
		 arrange(-value) %>% 
		 tail(20)
		 

```

education expenditure 


```{r}
education_vars=wbsearch(pattern="government.*education.*total.*gdp")
edu_budget_vars=wbsearch(pattern="government.*education.*total.*budget")
education_vars
```

```{r}
education <- wb(country="countries_only",indicator=c("SE.XPD.TOTL.GD.ZS"),mrv=1,gapfill=T)
edu.ind <- wb(country="IN",indicator=c("SE.XPD.TOTL.GD.ZS"),mrv=1)
edu.pk <- wb(country="PK",indicator=c("SE.XPD.TOTL.GD.ZS"),mrv=1)
edu_budget <- wb(country="countries_only",indicator=c("SE.XPD.TOTL.GB.ZS"),mrv=1,gapfill=T)

edu_reg <- wb(country="aggregates",indicator=c("SE.XPD.TOTL.GD.ZS"),mrv=1, cache=new_cache)
```

South Asian countries 

```{r}
south.asia <- c("BD","IN","PK","LK","AF","NP","BT","MV","MM")
edu.sa <- education %>% 
		 filter(iso2c %in% south.asia) %>% 
                 select(date,country, value) %>% 
		 arrange(-value)
edu.sa
```

```{r}
edu.budget.sa <- edu_budget %>% 
		 filter(iso2c %in% south.asia) %>% 
                 select(date,country, value) %>% 
		 arrange(-value)
edu.budget.sa
```




Top 20 countries 

```{r}
military %>% 
    select(date, iso2c,country, value) %>% 
		 arrange(-value) %>% 
		 slice(1:20)

```

Bottom 20 countries 

```{r}
military %>% 
    select(date, iso2c,country, value) %>% 
		 arrange(value) %>% 
		 slice(1:20)

```

```{r}
military %>% 
    select(date, iso2c,country, value) %>% 
		 arrange(-value) %>% 
		 tail(20)
		 

```

## GDP growth 

```{r}
gdp.growth <- wb(country="countries_only",indicator=c("NY.GDP.MKTP.KD.ZG"),mrv=5,gapfill=T)

```

### South Asia 

```{r}
south.asia <- c("BD","IN","PK","LK","AF","NP","BT","MV","MM")
gdp.growth.sa <- gdp.growth %>% 
		 filter(iso2c %in% south.asia) %>% 
                 select(date,country, value) %>% 
		 arrange(date)

```


Let's plot the data 

```{r}
gdp.growth.sa %>% 
    ggplot() +
    geom_col(aes(date,value)) +
    facet_wrap(~country) +
    labs(x="Year", y="GDP growth") + 
    theme_minimal() +  
    theme(strip.text.x=element_text(size=16,color="black"))+  
    theme(strip.background=element_rect(fill="grey"))
```

```{r}
ggsave("~/Pictures/gdg_growth_sa.png")
```

