class: inverse,middle,center 

# ggformula vignette

---

class: split-three

<!--column 1-->

.column[
.split-two[
.row[

```{r, include=F}
diamonds2 <- diamonds %>% 
  filter(color == "D" | color == "J") %>%
  mutate(col = as.character(color))
```

```{r,fig.asp=.57}
gf_boxplot(price ~ col, data= diamonds2) %>%  
       gf_theme(theme_bw())
```
]

.row[

```{r,fig.asp=.57}
gf_violin(price ~ col, data= diamonds2) %>%  
       gf_theme(theme_bw())
```
]

]]


<!--column 2-->

.column[
.split-two[
.row[

```{r,fig.asp=.57}
gf_boxplot(price ~ col, data= diamonds2) %>%  
gf_violin(price ~ col, data= diamonds2) %>%  
       gf_theme(theme_bw())
```
]

.row[

```{r,fig.asp=.57}
gf_boxplot(price ~ col, data= diamonds2, alpha=0.05) %>%  
gf_violin(price ~ col, data= diamonds2, col=NA, fill="navy", alpha=0.3) %>%  
       gf_theme(theme_bw())
```
]

]]

<!--column 3-->

.column[
.split-two[
.row[

```{r,fig.asp=.57}
gf_boxplot(price ~ col, data= diamonds2, alpha=0.05) %>%  
gf_violin(price ~ col, data= diamonds2, col=NA, fill=~col, alpha=0.3) %>%  
       gf_theme(theme_bw())
```
]

.row[

a bit of help

```{r, message = T}
gf_violin()
```
]

]]


---

class: split-40 

<!--column 1-->

.column [
.split-two[
.row[
```{r,fig.asp=.57}
gf_violin(price ~ col, data=diamonds2,
	  color=~col, fill=~col, alpha=0.2,
	  scale="count",
	  draw_quantiles=c(0.25,0.5,0.75),size=0.8,
	  adjust=1/2
	  ) %>% 
       gf_theme(theme_bw())
```
]

]]

<!--column 2-->

.column[
.split-two[
.row[
```{r, fig.asp=.61}
gf_point(price ~ carat | col, data = diamonds2, alpha = 0.2) %>%
  gf_lm() %>% 
       gf_theme(theme_bw())
```
]

.row[
```{r, fig.asp=.51}
gf_point(price ~ carat | col ~ clarity, data = diamonds2, alpha = 0.2) %>%
  gf_lm()%>% 
       gf_theme(theme_bw())
```
]


]]



---

class: split-three

<!--column 1-->

.column[
.split-two[
.row[
```{r,fig.asp=.57}
p1 <- gf_point(price ~ carat, data = diamonds2, 
         color = ~ col, alpha = 0.2, size = 0.5)  %>% 
         gf_theme(theme_minimal())
p1
```

]

.row[

```{r,fig.asp=.57}
p2 <- p1 %>% 
         gf_lm(alpha=0.5)  
p2
```
]

]]

<!--column 2-->

.column[
.split-two[
.row[
```{r, fig.asp=.57}
p3 <- p2  %>% 
	 gf_facet_wrap(~color) 
p3
```

]

.row[

```{r, fig.asp=.57}
p4 <- p3  %>%  
     gf_labs(title = "Price vs Size", subtitle = "(2 colors of diamonds)",
          caption = "source: ggplot2::diamonds",
          x = "size (carat)", y = "price (US dollars)") 
p4
```
]

]]

<!--column 3-->

.column[
.split-two[

.row[
```{r, fig.asp=.57}
p5 <- p4 %>% 
       gf_refine(scale_color_manual(values = c("red", "navy"))) 
p5
```

]

.row[
```{r, fig.asp=.57}
p6 <- p5 %>% 
       gf_refine(scale_color_manual(values = c("red", "navy"), guide = "none"))
p6

```
]

]]


---

class: split-three

<!--column 1-->

.column[
.split-two[
.row[
```{r,fig.asp=.57}
mtcars2 <- df_stats(wt ~ cyl, data = mtcars, median_wt = median)
     gf_point(wt ~ hp, size = ~wt, color = ~cyl, data = mtcars) %>%
       gf_abline(slope = ~0, intercept = ~median_wt, color = ~cyl, data = mtcars2) %>% 
       gf_theme(theme_bw())
```
]
.row[
```{r ,fig.asp=.57}
# avoid warnings by using formulas:
     gf_point(wt ~ hp, size = ~wt, color = ~cyl, data = mtcars) %>%
       gf_abline(slope = ~0, intercept = ~3, color = "green") %>% 
       gf_theme(theme_bw())
```
]

]]
 

<!--column 2-->

.column[
.split-two[
.row[
```{r , fig.asp=.57}
gf_point(mpg ~ hp, color = ~cyl, size = ~wt, data = mtcars) %>%
       gf_abline(color = "red", slope = ~ - 0.10, intercept = ~ 35) %>% 
       gf_theme(theme_bw())
```
]

.row[
```{r, fig.asp=.57 }
gf_point(mpg ~ hp, color = ~cyl, size = ~wt, data = mtcars) %>%
       gf_abline(
         color = "red", slope = ~slope, intercept = ~intercept,
         data = data.frame(slope = -0.10, intercept = 33:35)
       ) %>% 
       gf_theme(theme_bw())

```
]

]]
 

<!--column 3-->

.column[
.split-two[
.row[
```{r , fig.asp=.57}
gf_point(mpg ~ hp, color = ~cyl, size = ~ wt, data = mtcars) %>%
       gf_hline(color = "navy", yintercept = ~ c(20, 25), data = NA) %>%
       gf_vline(color = "brown", xintercept = ~ c(200, 300), data = NA) %>% 
       gf_theme(theme_bw())

```
]
.row[
```{r , fig.asp=.57}
gf_point(mpg ~ hp, size = ~wt, data = mtcars, alpha = 0.3) %>%
       gf_hline(color = ~"horizontal", yintercept = ~ c(20, 25), data = NA) %>%
       gf_vline(color = ~"vertical", xintercept = ~ c(100, 200, 300), data = NA) %>% 
       gf_theme(theme_bw())
```
]

]]

---

class: split-three

<!--column 1-->

.column[
.split-two[
.row[
```{r,fig.asp=.57}
data(Runners, package = "mosaicModel")
Runners <- Runners %>% filter( ! is.na(net))
gf_density(~ net, data = Runners)
```
]
.row[
```{r,fig.asp=.57}
gf_density( ~ net,  fill = ~ sex,  alpha = 0.5, data = Runners)
```
]

]]

<!--column 2-->

.column[
.split-two[
.row[
```{r,fig.asp=.57}
# gf_dens() is similar, but there is no line at bottom/sides, and it is not "fillable"
gf_dens( ~ net, color = ~ sex, alpha = 0.7, data = Runners)    
```
]
.row[
```{r,fig.asp=.57}
```
]

]]



---

class: inverse,middle,center 

# `gf_fun()`

---

class: split-four

<!--column 1-->

.column[
.split-three[
.row[
```{r,fig.asp=.57}
gf_function(fun = sqrt, xlim = c(0, 10)) %>% 
       gf_theme(theme_bw())
```
]
.row[
```{r,fig.asp=.57}
gf_fun(x^2 ~ x, xlim = c(-4,4)) %>% 
       gf_theme(theme_bw())
```
]
.row[
```{r,fig.asp=.57}
sqr <- makeFun(x^2 ~ x)
gf_function(fun=sqr, xlim = c(-4,4)) %>% 
       gf_theme(theme_bw())
```
]

]]

<!--column 2-->

.column[
.split-three[
.row[
```{r,fig.asp=.57}
gf_function(fun = sqrt, xlim = c(0, 10)) %>% 
       gf_theme(theme_bw())
```
]
.row[
```{r,fig.asp=.57}
gf_fun(x^2 ~ x, xlim = c(-4,4)) %>% 
       gf_theme(theme_bw())
```
]
.row[
```{r,fig.asp=.57}
sqr <- makeFun(x^2 ~ x)
gf_function(fun=sqr, xlim = c(-4,4)) %>% 
       gf_theme(theme_bw())
```
]

]]

---

class: inverse,middle,center 

# `gf_dist()` 

---

class: split-three

<!--column 1-->

.column[
.split-two[
.row[
```{r,fig.asp=.57}
gf_dist("norm") %>% 
    gf_theme(theme_bw())
```
]

.row[
```{r,fig.asp=.57}
gf_dist("norm", color="red") %>% 
    gf_theme(theme_bw())
```
]


]]

<!--column 2-->

.column[
.split-two[

.row[
```{r,fig.asp=.57}
gf_dist("norm", mean=10, sd=2) %>% 
    gf_theme(theme_bw())

```
]

.row[
```{r,fig.asp=.57}
gf_dist("norm", mean=10, sd=2, type="cdf") %>% 
    gf_theme(theme_minimal())

```
]
.row[
```{r,fig.asp=.57}
gf_dist("norm", mean=10, sd=2, color="blue", type="cdf") %>% 
    gf_theme(theme_minimal())
```
]

]]

<!--column 3-->

.column[
.split-two[

.row[
```{r,fig.asp=.57}
gf_dist("norm", mean=10, sd=2, fill="green", kind="histogram") %>% 
    gf_theme(theme_minimal())

```
]

.row[
```{r,fig.asp=.57}
gf_dist("norm", mean=10, sd=2, fill="grey", kind="histogram") %>% 
gf_dist("norm", mean=10, sd=2) %>% 
    gf_theme(theme_minimal())
```
]

]]

---

class: split-three

<!--column 1-->

.column[
.split-two[
.row[
```{r,fig.asp=.57}
gf_dist("norm", color="red", kind="qqstep", resolution=15) %>% 
    gf_theme(theme_minimal())


```
]

.row[
```{r,fig.asp=.57}
gf_dist("norm", color="red", kind="qqstep", resolution=50) %>% 
    gf_theme(theme_minimal())


```
]


]]

<!--column 2-->

.column[
.split-two[

.row[
```{r,fig.asp=.57}
gf_dist("t", df=9) %>% 
    gf_theme(theme_minimal())
```
]

.row[
```{r,fig.asp=.57}
gf_dist("norm",color="red") %>% 
gf_dist("t", df=9, color="blue") %>% 
    gf_theme(theme_minimal())
```

]

]]

<!--column 3-->

.column[
.split-two[

.row[
```{r,fig.asp=.57}
gf_dist("binom", size=20,prob=0.25) %>% 
    gf_theme(theme_minimal())
```
]
.row[
```{r,fig.asp=.57}
gf_dist("binom", size=20,prob=0.25, plot_size=2) %>% 
    gf_theme(theme_minimal())
```
]

]]

---

class: split-three

<!--column 1-->

.column[
.split-two[
.row[
```{r,fig.asp=.57}
gf_dist("exp") %>% 
    gf_theme(theme_minimal())
```
]

.row[
```{r,fig.asp=.57}
gf_dist("f", df1=99, df2=45) %>% 
    gf_theme(theme_minimal())
```
]


]]

<!--column 2-->

.column[
.split-two[

.row[

```{r,fig.asp=.57}
gf_dist("pois", lambda=1) %>% 
    gf_theme(theme_minimal())
```
]

.row[
```{r,fig.asp=.57}
gf_dist("chisq", df=99) %>% 
    gf_theme(theme_minimal())
```

]

]]

<!--column 3-->

.column[
.split-two[

.row[
```{r,fig.asp=.57}
gf_dist("norm", type="pp" ) %>% 
    gf_theme(theme_minimal())

```
]

.row[
```{r,fig.asp=.57}
alpha <- c(.05,.95)
rcrit <- round(qnorm(alpha),2)
gf_dist("norm", fill = ~ (abs(x) <= rcrit[2]), geom = "area") %>% 
    gf_refine(
	      scale_fill_manual(values=c("red","blue")),
	      scale_x_continuous(breaks = c(rcrit[1],0,1.64)),
	      mytheme2
    )
```
]

]]



