---
title: "Historic 7th March speech of Sheikh Mujibur Rahman in wordcloud"
author: "Rushad Faridi"
date: '2018-03-07'
tags: []
categories: []
---

```{r,echo=FALSE}
library(knitr)
opts_chunk$set(comment=NA,warning=FALSE,message=FALSE)
```


In one of my previous posts, I have ventured into creating a word cloud from some tutorial. Now since today is 7th March, the historic day when the founder of Bangladesh,[Sheikh Mujibur Rahman](http://https://en.wikipedia.org/wiki/Sheikh_Mujibur_Rahman "Sheikh Mujibur Rahman") , delivered a speech which greatly energized the nation before the Independence war broke out few days later.

The speech in Bengali can be found in [Bangla Wikipedia](http://https://bn.wikipedia.org/wiki/%E0%A6%B8%E0%A6%BE%E0%A6%A4%E0%A6%87_%E0%A6%AE%E0%A6%BE%E0%A6%B0%E0%A7%8D%E0%A6%9A%E0%A7%87%E0%A6%B0_%E0%A6%AD%E0%A6%BE%E0%A6%B7%E0%A6%A3 "Bangla Wikipedia"). I just copied the text into a text file. We will just take it from there and see how it goes.

First I will import the text into R:

```{r imp  }
speech <- readLines("../RAWDATA/sheikh_mujib_7th_March_speech.txt")
```

Now I will create a variable call line number recording number of line for each sentence. 

Now let's create a data frame with line number and the speech text. We use `stringsAsFactors=F` to prevent turning the text into `factor`.

```{r}
speech.df <- data.frame(line=1:length(speech), 
                        text=speech, 
                        stringsAsFactors = F)
```

We observe there are some empty rows, let's get rid of those:

```{r}
library(dplyr)
speech.df.clean <- speech.df %>%
                    filter(!text=="")
```

Now the sentences are into data frame we are ready to break those down into words.

```{r}
library(tidytext)
tidy_speech <- speech.df.clean %>%
                  unnest_tokens(word, text)
save(tidy_speech, file="../RDATA/tidy_speech.RData")
```


Now we can see which words were most frequently used:

```{r}
tidy_speech %>%
  count(word, sort=TRUE)
```

Now let's create the `wordcloud`.

```{r}
library(wordcloud)
```

After loading the required package, here in the following, we have the word cloud

```{r}
tidy_speech %>%
  count(word) %>%
  with(wordcloud(word,n, max.words = 100))
```

Now this wordcloud might be distorted due to presence of some words which are pretty commonly used and usually needed to be removed. Let's create manually such data frame. 

```{r}
stop.words <- c("আমি", "আমার", "করে", "যে", "আমাকে", "তাকে", "তিনি", "এই", "আছে","আর", "হয়েছে", "আমরা","যে", "আমাদের","যদি","না","হবে", "আপনারা" )
stop_words <- data.frame(sl=1:length(stop.words), 
                         word=stop.words,
                         stringsAsFactors = F)
```

Now time to remove those stop words. 

```{r}
clean_speech <- tidy_speech %>%
                 anti_join(stop_words)
save(clean_speech, file="../RDATA/clean_speech.RData")
```

After removing these words, here is the new word cloud:

```{r}
clean_speech %>%
  count(word ) %>%
  with(wordcloud(word,n,max.words = 100))
```

