---
title: World Justice Score importing data
author: ~
date: '2018-03-03'
slug: world-justice-score-import-data
cateogories: []
tags: []
---


first let's load the library

```{r llib  }
library(readxl)
library(dplyr)
library(tidyr)
library(janitor)
```


let's first load the data

```{r lload  }
 import.file <- read_excel("../RAWDATA/FINAL_2017-2018_wjp_rule_of_law_index_HISTORICAL_DATA_FILE.xlsx",
		       sheet=6)
```

When I first started to work, I thought I will just work with limited set of data, may be 1 and 4 th row only. But later on I thought it worked so well that the follwoing threee liner is good enough to pull off all the hard work. 

```{r os  }
wjs.score <- import.file %>% 
		  gather(country, rol.ind,-Country) %>% 
		  spread(Country,rol.ind) 
```


It seems that right now the data is pretty ripe for using `janitor` package functions.

```{r nt  }
wjs.score.clean <- clean_names(wjs.score) %>% 
                   remove_empty_cols() %>% 
		   remove_empty_rows()
```

Now let's save the data

```{r ss  }
save(wjs.score.clean, file="../RDATA/wjs_score_clean.RData")
```

In the next post we are going see some analyis out of this data.

